Lens Modeling in \sw

### 2014-01-16 text/ms.tex
editing appendix

First let us recall the formulas for comoving distances.
\begin{equation}
D = \int \frac{dz}{\sqrt{\Omega_m(1+z)^3 + \Omega_\Lambda}}
\end{equation}
The comoving distances from observer to lens, from lens to source, and
from observer to source are given as follows:
\begin{equation}
\begin{aligned}
&D_S    &                                &\int_0^{z_S} \\
\noalign{\medskip}
&D_{LS} & = \frac c{H_0} \ \times \quad  &\int_{z_L}^{z_S} \\
\noalign{\medskip}
&D_L    &                                &\int_0^{z_L}
\end{aligned}
\end{equation}
Angular-diameter distances $d$ can be related to comoving distances
$D$ by:
\begin{equation}
\begin{aligned}
D_S &= (1+z_S) \, d_S \\
D_{LS} &= \frac{1+z_S}{1+z_L} \, d_{LS} \\
D_L &= (1+z_L) \, d_L
\end{aligned}
\end{equation}
Angular-diameter distances are always smaller than comoving distances.

Locations on the lens plane in angular coordinates on the sky, are
expressed as
\begin{equation}
(x,y) = d_L (\theta_x,\theta_y) \,.
\end{equation}

>>>>

First let us recall various distance formulas. Comoving distances
involve integrals of the type
\begin{equation}
D = \int \frac{dz}{\sqrt{\Omega_m(1+z)^3 + \Omega_\Lambda}}
%\raise.5ex\hbox{.}
\end{equation}
Specifically, the comoving distance $D_S$ from observer to source,
$D_{LS}$ from lens to source, and $D_L$ from observer to lens are
given by the above integral, with limits as follows.
\begin{equation}
\begin{aligned}
&D_S    &                                &\int_0^{z_S} \\
\noalign{\medskip}
&D_{LS} & = \frac c{H_0} \ \times \quad  &\int_{z_L}^{z_S} \\
\noalign{\medskip}
&D_L    &                                &\int_0^{z_L}
\end{aligned}
\end{equation}
Angular-diameter distances $d$ can be related to comoving distances
$D$ by scale factors, as follows.
\begin{equation}
\begin{aligned}
D_S &= (1+z_S) \, d_S \\
D_{LS} &= \frac{1+z_S}{1+z_L} \, d_{LS} \\
D_L &= (1+z_L) \, d_L
\end{aligned}
\end{equation}
Consequently, angular-diameter distances are always smaller than
comoving distances.  Moreover, while comoving distances can be simply
added, angular distances cannot:
\begin{equation}
d_S \neq d_L + d_{LS}
\end{equation}

Locations on the lens plane in angular coordinates on the sky, are
expressed as
\begin{equation}
(x,y) = d_L (\theta_x,\theta_y)
\end{equation}
